---
title: "Reveal.js demo"
author: Andrew Caines
date: 27th October 2014
output: revealjs::revealjs_presentation
---

# How it works
- Rmarkdown package: `devtools::install_github("rstudio/rmarkdown")`
- revealjs package: `devtools::install_github("jjallaire/revealjs")`
- specify revealjs_presentation at head of .Rmd file: `revealjs::revealjs_presentation`
- make .html file with R(script): `render('foo.Rmd', revealjs_presentation(options))`


# Headers
- 2 levels: `# h1, ## h2`

# h1 = new slide

## h2 = subheader


# Options
- themes: `default (black-on-white), simple, sky...`
- transitions: `default (spin), cube, page, concave...`
- also: vertical centering, syntax highlighting, incremental bullet points


# Incremental bullets
> - bullet 1 `> - bullet 1`
> - bullet 2 `> - bullet 2`
> - make all bullets incremental: render with option `incremental = TRUE`


# Pros and Cons

## +ve
- shallow learning curve
- formatting simplicity
- web-ready
- progress bar
- inline R code

## -ve
- permanence?
- slower development
- lack of formatting sophistication


# inline R code (no output)
```{r, eval = FALSE}
summary(cars)
```


# code plus output
```{r}
summary(cars)
```


# output only
```{r, echo = FALSE}
summary(cars)
```


# plots
```{r, echo = FALSE}
plot(cars)
```


# n.b. Slidify
http://ramnathv.github.io/slidify/
