---
title: "Reveal.js demo"
author: Andrew Caines
date: 27th October 2014
output: 
  revealjs_presentation:
    theme: default
    transition: fade
    highlight: default
    center: false
---

# How it works
> - spoken language [incremental bullets]
> - error analysis
> - data quality


# Code demo
## etc
1. transcriptions
2. annotation
3. parsing experiments


---

# Future Work
## What we'd like to do
1. conform to xml standard; e.g. Ide & Suderman 2014 Linguistic Annotation Framework
2. decide what to annotate, label names, principles
3. inter-annotator agreement exercise
4. IPA in transcription

----

+ new slide without header
+ render in R:
```
# devtools::install_github("rstudio/rmarkdown")
library(rmarkdown)
setwd('Dropbox/workspace/gitHub/ALTA/presentations/year1end/')
render('dtalyear1.Rmd')
```

----

+ code plus output
```{r}
summary(cars)
```

----

+ output only
```{r, echo = FALSE}
summary(cars)
```

----

+ plot
```{r, echo = FALSE}
plot(cars)
```

----

+ code (no output)
```{r, eval = FALSE}
plot(cars)
```
